Monte Carlo and bootstrap for ALL parameters with tables

### 2024-09-08 Last_tables/All3_tab_algo7.Rmd
L U and uniform sampling

colnames(df_total1) <- c("Parameter of interest", "Method", "Coverage rate", "Lower part", "Upper part", "Mean length")
```

@@

colnames(df_total2) <- c("Parameter of interest", "Method", "Coverage rate", "Lower part", "Upper part", "Mean length")
```

>>>>

colnames(df_total1) <- c("Parameter of interest", "Method", "Coverage rate", "L", "U", "Mean length")
```

@@

colnames(df_total2) <- c("Parameter of interest", "Method", "Coverage rate", "L", "U", "Mean length")
```

### 2024-09-08 Last_tables/All3_tab_unif.Rmd
L U and uniform sampling

In this document, \textbf{sampling through a grid} is used to create a sample, more precisely \textbf{algorithm 8}, and \textbf{three concentric circles} are used to compute local variables.

@@

# Example: Algorithm 8 with basic bootstrap

```{r}
fun_samp <- sampling_grid3
```

@@

```{r RS_algo8}
tab_rs <- DF_rs %>%
  kable("latex", booktabs = FALSE, align = "lc", linesep = c("", "", "",
  "\\hline"), caption = paste0("Relative stability of variance by using ", B1, " Monte Carlo iterations and ", B2, " bootstrap replications"), col.names = gsub("[.]", " ", names(DF_rs))) %>% # \\hline \\addlinespace
  kable_styling(latex_options = c("striped", "hold_position")) %>% # bootstrap_options = "striped", full_width = FALSE, 
  row_spec(0, bold = TRUE) %>% # , hline_after = TRUE
  row_spec(c(0, 4, 8), hline_after = T) %>% 
  collapse_rows(columns = 1, latex_hline = "major")
```

@@

```{r CI_tot_algo8}
tab_ci1 <- df_total1 %>%
  kable("latex", booktabs = FALSE, align = "llcccc", caption = paste0("Characteristics of confidence intervals when using ", B1, " Monte Carlo iterations and ", B2, " bootstrap replications (totals)")) %>%
  kable_styling(latex_options = "hold_position") %>%
  row_spec(0, bold = TRUE) %>%
  row_spec(c(0, 16), hline_after = T) %>% 
  row_spec(c(16), hline_after = T) %>% 
  collapse_rows(columns = 1, valign = "middle")
```

@@

```{r CI_ratio_algo8}
tab_ci2 <- df_total2 %>%
  kable("latex", booktabs = FALSE, align = "llcccc", caption = paste0("Characteristics of confidence intervals when using ", B1, " Monte Carlo iterations and ", B2, " bootstrap replications (ratios)")) %>%
  kable_styling(latex_options = "hold_position") %>%
  row_spec(0, bold = TRUE) %>%
  row_spec(c(0), hline_after = T) %>% 
  # row_spec(c(16,32), hline_after = T) %>% 
  collapse_rows(columns = 1, valign = "middle")
```

@@

```{r RB_algo8}
tab_var <- diff_var %>%
  kable("latex", booktabs = FALSE, align = "lc", linesep = c("", "", "",
  "\\addlinespace"), caption = paste0("Approximation of Relative Bias when using ", B1, " Monte Carlo iterations and ", B2, " bootstrap replications in one case and ", B0, " Monte Carlo iterations in the other case"), col.names = gsub("[.]", " ", names(diff_var))) %>% # \\hline
  kable_styling(latex_options = c("striped", "hold_position")) %>% # bootstrap_options = "striped", 
  row_spec(0, bold = TRUE) %>% # , hline_after = TRUE
  row_spec(c(0, 4, 8), hline_after = T) %>% 
  collapse_rows(columns = 1, latex_hline = "major")
```

>>>>

In this document, \textbf{uniform sampling} is used to create a sample and \textbf{three concentric circles} are used to compute local variables.

@@

# Example: Algorithm 6 with basic bootstrap

```{r}
fun_samp <- sampling_unif
```

@@

```{r RS_unif}
tab_rs <- DF_rs %>%
  kable("latex", booktabs = FALSE, align = "lc", linesep = c("", "", "",
  "\\hline"), caption = paste0("Relative stability of variance by using ", B1, " Monte Carlo iterations and ", B2, " bootstrap replications"), col.names = gsub("[.]", " ", names(DF_rs))) %>% # \\hline \\addlinespace
  kable_styling(latex_options = c("striped", "hold_position")) %>% # bootstrap_options = "striped", full_width = FALSE, 
  row_spec(0, bold = TRUE) %>% # , hline_after = TRUE
  row_spec(c(0, 4, 8), hline_after = T) %>% 
  collapse_rows(columns = 1, latex_hline = "major")
```

@@

```{r CI_tot_unif}
tab_ci1 <- df_total1 %>%
  kable("latex", booktabs = FALSE, align = "llcccc", caption = paste0("Characteristics of confidence intervals when using ", B1, " Monte Carlo iterations and ", B2, " bootstrap replications (totals)")) %>%
  kable_styling(latex_options = "hold_position") %>%
  row_spec(0, bold = TRUE) %>%
  row_spec(c(0, 16), hline_after = T) %>% 
  row_spec(c(16), hline_after = T) %>% 
  collapse_rows(columns = 1, valign = "middle")
```

@@

```{r CI_ratio_unif}
tab_ci2 <- df_total2 %>%
  kable("latex", booktabs = FALSE, align = "llcccc", caption = paste0("Characteristics of confidence intervals when using ", B1, " Monte Carlo iterations and ", B2, " bootstrap replications (ratios)")) %>%
  kable_styling(latex_options = "hold_position") %>%
  row_spec(0, bold = TRUE) %>%
  row_spec(c(0), hline_after = T) %>% 
  # row_spec(c(16,32), hline_after = T) %>% 
  collapse_rows(columns = 1, valign = "middle")
```

@@

```{r RB_unif}
tab_var <- diff_var %>%
  kable("latex", booktabs = FALSE, align = "lc", linesep = c("", "", "",
  "\\addlinespace"), caption = paste0("Approximation of Relative Bias when using ", B1, " Monte Carlo iterations and ", B2, " bootstrap replications in one case and ", B0, " Monte Carlo iterations in the other case"), col.names = gsub("[.]", " ", names(diff_var))) %>% # \\hline
  kable_styling(latex_options = c("striped", "hold_position")) %>% # bootstrap_options = "striped", 
  row_spec(0, bold = TRUE) %>% # , hline_after = TRUE
  row_spec(c(0, 4, 8), hline_after = T) %>% 
  collapse_rows(columns = 1, latex_hline = "major")
```
